Joint Satellite Distributions in the Local Group

### 2017-10-02 paper/paper.tex
one more plot
+1 paragraph alignments + cosmic web

@@

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{mu_lg.pdf}
\includegraphics[width=0.7\textwidth]{planewidth_lg.pdf}
\includegraphics[width=0.7\textwidth]{ca_ratio_lg.pdf}
\includegraphics[width=0.7\textwidth]{ba_ratio_lg.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:general}}
\end{figure*}

>>>>

We characterize the alignment between the satellite plane and the
vector connecting the two dominant galaxies as $\mu=|\hat{r}_{AB}\cdot
\hat{n}|$. 
It has been shown that LG pair separation vector is aligned along the
filaments in  which they are typically embeded
\cite{2015ApJ...799...45F}, the LG pairs found in pancake-like DM
matter arrangements are aligned with the plane itself. 
Characterizing the satellite alignments with $\mu$ thus provide
information about how satellites are distributed with respect to the
cosmic web.

@@

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{scatter_width.pdf}
\includegraphics[width=0.7\textwidth]{scatter_mu.pdf}
\includegraphics[width=0.7\textwidth]{scatter_ca_ratio.pdf}
\includegraphics[width=0.7\textwidth]{scatter_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:general}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{distribution_width.pdf}
\includegraphics[width=0.7\textwidth]{distribution_mu.pdf}
\includegraphics[width=0.7\textwidth]{distribution_ca_ratio.pdf}
\includegraphics[width=0.7\textwidth]{distribution_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:general}}
\end{figure*}
